Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-04-02 bbbq_article.tex
Redo figure 1D for our study, progress #192

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.95\textwidth]{bbbq_1_smart_results/fig_f_tmh_2_panel}
  \caption{
    TMH-derived peptides are predicted to be over-presented in general,
    which is for MHC-I (left column) and MHC-II (right column),
    as well as for the proteomes of SARS-CoV-2 (top row), human (middle 
    row) and \emph{M. tuberculosis} (bottom row).
    The bars show the percentage of epitopes predicted to be 
    overlapping with TMHs.
    The red lines indicate the percentage as expected by chance.
    See supplementary tables \ref{tab:tmh_binders_mhc1} and \ref{tab:tmh_binders_mhc2}
    for the exact TMH and  epitope counts.
    \richel{Add panel with hydrophobicity?}
  }
  \label{fig:bbbq_1_smart_results}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.9\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_f_tmh_2_panel.png}
    \label{fig:bbbq_1_smart_results}
  \end{subfigure}

  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_hydrophobicity_mhc1.png}
    \label{fig:hydrophobicity_2}
  \end{subfigure}  
  \hfill
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_hydrophobicity_mhc2.png}
    \label{fig:hydrophobicity_2}
  \end{subfigure}  
  \caption{
    \textbf{(A)} 
    TMH-derived peptides are predicted to be over-presented in general,
    which is for MHC-I (left column) and MHC-II (right column),
    as well as for the proteomes of SARS-CoV-2 (top row), human (middle 
    row) and \emph{M. tuberculosis} (bottom row).
    The bars show the percentage of epitopes predicted to be 
    overlapping with TMHs.
    The red lines indicate the percentage as expected by chance.
    See supplementary tables \ref{tab:tmh_binders_mhc1} and \ref{tab:tmh_binders_mhc2}
    for the exact TMH and  epitope counts.
    \textbf{(B)} and \textbf{(C)}:
    The relation between the percentage of TMH-derived epitopes presented,
    and the hydrophobicity score of binders for MHC-I haplotypes (panel B)
    and MHC-II haplotypes (panel C). Trendline assumes a linear relationship.
  }
\end{figure}
